\documentclass[letterpaper,11pt]{article}

% =======================
%   PACKAGE INCLUDES
% =======================
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% =======================
%   PAGE SETUP
% =======================
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[top=0.2in, bottom=0.3in, left=0.3in, right=0.3in]{geometry}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% =======================
%   CUSTOM COMMANDS
% =======================

% Bullet point for resume items
\newcommand{\resumeItem}[1]{
  \item[\vcenter{\hbox{\tiny$\bullet$}}] \small{#1 \vspace{-2pt}}
}

% Subheading for jobs/education
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

% Simple subheading for certificates
\newcommand{\resumeSimpleSubheading}[2]{
  \item \textbf{#1} \hfill \textit{\small #2} \vspace{-3pt}
}

% Project subheading
\newcommand{\resumeProjectSimple}[2]{
  \item \textbf{#1} \hfill \textit{\small #2} \vspace{-3pt}
}

% List environments for items and subheadings
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% =======================
%   DOCUMENT START
% =======================

\begin{document}

% ----- NAME & CONTACT -----
\begin{center}
    \textbf{\Huge \scshape Syed Nameer Ali}
\end{center}
\begin{center}
  \small
  (+92)-335-2929504 $|$
  \href{mailto:s.nameer18606@gmail.com}{\underline{s.nameer18606@gmail.com}} $|$
  \href{https://www.linkedin.com/in/syednameerali/}{\underline{linkedin.com/in/syednameerali}} $|$
  \href{https://github.com/NameerAli}{\underline{github.com/NameerAli}}
\end{center}

% =======================
%   EDUCATION
% =======================
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://www.iba.edu.pk/}{Institute of Business Administration (IBA)}}
    {Karachi, PK}
    {B.S. Computer Science}
    {Aug. 2019 -- Jun. 2023}
    \resumeItemListStart
      \resumeItem{Relevant Courses: Statistical Inference, Data Mining, Data Warehousing, Computer Vision, Algorithms, Design Patterns, Web Application Development, Business Intelligence.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% =======================
%   EXPERIENCE
% =======================
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.pingkode.com/}{PingKode}}
      {Karachi, PK}
      {Software Engineer}
      {Aug. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing backend systems with \textbf{Django} for a medical appointment booking platform, integrating secure authentication, appointment scheduling, and user management.}
        \resumeItem{Integrating a conversational AI chatbot into an existing HRMS web application using \textbf{LangChain}, enabling real-time candidate and employee queries through natural language understanding.}
      \resumeItemListEnd

  \resumeSubheading
    {\href{https://www.sofstica.com/}{Sofstica Solutions PVT. LTD}}
    {Karachi, PK}
    {Software Engineer AI}
    {Oct. 2023 -- July 2025}
    \resumeItemListStart
      \resumeItem{Engineered and deployed \href{https://www.innohlth.ai}{\textbf{RRS-Copilot}}, an intelligent agentic AI system validated on the \textbf{MIMIC FHIR dataset}, achieving \textbf{87\% sensitivity} in predicting clinical deterioration and delivering \textbf{6-hour advance alerts} to healthcare professionals, potentially preventing critical patient outcomes.}
      \resumeItem{Developed LLM-powered clinical decision support system using \textbf{LangGraph} for multi-step reasoning and \textbf{FastAPI} for deployment, reducing false-positive alerts by 42\% compared to standard rule-based clinical scoring systems over 6-month pilot study.
}
      \resumeItem{Architected and developed the \textbf{{Provider In}tegrated System (PIS)}, an enterprise-grade middleware solution using \textbf{Spring Boot} that enables seamless interoperability across major EHR providers including \textbf{Cerner, Epic, and Meditech}, supporting both \textbf{HL7v2 and FHIR} standards for real-time and request-response healthcare data exchange.}
    \resumeItemListEnd
\resumeSubheading
    {\href{https://folio3.com/}{Folio3 PVT. LTD}}
    {Karachi, PK}
    {Artificial Intelligence Intern}
    {Jul. 2022 -- Aug. 2022}
    \resumeItemListStart
        \resumeItem{Developed a real-time \textbf{\href{https://github.com/ZohairAbbas/Number-Plate-Detection}{number plate recognition system}} with \textbf{YOLOv5 + OCR}, achieving 88\% accuracy and 50\% faster processing.}
        \resumeItem{Built ML pipelines for data cleaning, feature engineering, training, and evaluation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% =======================
%   PROJECTS
% =======================
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectSimple
    {\href{https://github.com/nameerali/courtconnect}{CourtConnect – Indoor Sports Court Booking Platform}}
    {2025}
    \resumeItemListStart
      \resumeItem{Built a full-stack app \textbf{(Django/DRF} + \textbf{Next.js}) with \textbf{JWT} auth, role-based access (Player/Owner/Admin), court management, and search/filters.}
      \resumeItem{Implemented conflict-free time-slot booking and availability APIs; Stripe payments/webhooks in progress.}
    \resumeItemListEnd
    
  \resumeProjectSimple
    {\href{https://github.com/saadhzubairi/FYP-TalentHive}{Talent Hive – AI-powered HR Management System (FYP)}}
    {Spring 2023}
    \resumeItemListStart
      \resumeItem{Engineered a full-stack Human Resource Management System to streamline recruitment workflows for HR departments.}
      \resumeItem{Built a custom \textbf{SpaCy Named Entity Recognition (NER)} model for intelligent resume parsing and auto-tagging.}
      \resumeItem{Integrated candidate scoring, resume ranking, and structured profile visualization to enhance decision-making.}
    \resumeItemListEnd

  \resumeProjectSimple
    {\href{https://github.com/NameerAli/PaperTalk-Chat-with-PDFs}{PaperTalk – Chat with PDFs}}
    {2023}
    \resumeItemListStart
      \resumeItem{Built a conversational PDF assistant using \textbf{LangChain, Streamlit, ChatGPT, and Hugging Face LLMs}.}
      \resumeItem{Optimized backend with multithreading and vector embeddings, reducing response time by \textbf{40\%}.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% =======================
%   CERTIFICATIONS
% =======================
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item{
      \textbf{Datacamp}{: \href{https://www.datacamp.com/statement-of-accomplishment/course/51881279c5ea4895768177f9660af650dbd09545}{Intermediate SQL}, 
      \href{https://www.datacamp.com/statement-of-accomplishment/course/1734f2afa864fac67a97598d78957d6886265d9f}{Intermediate Python}, 
      \href{https://www.datacamp.com/completed/statement-of-accomplishment/course/92a798aaa98b0b56b4ddabd0e10f520a70cd66e4}{Understanding Machine Learning}}
      \\
      \textbf{Coursera}{: \href{https://www.coursera.org/account/accomplishments/certificate/U27GDBJEHSXG}{AI For Everyone}, 
      \href{https://www.coursera.org/account/accomplishments/certificate/6U94DU6JQ49H}{Foundations of Data Science}, Machine Learning Specialization}
      \\
      \textbf{Kaggle}{: \href{https://www.kaggle.com/learn/certification/syednameerali/intro-to-machine-learning}{Intro to Machine Learning}, 
      \href{https://www.kaggle.com/learn/certification/syednameerali/intermediate-machine-learning}{Intermediate Machine Learning}}
    }
  }
\end{itemize}

% =======================
%   SKILLS & INTERESTS
% =======================
\section{Skills \& Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item{
      \textbf{Programming Languages:} Java, Python, SQL \\
      \textbf{Web \& API Development:} FastAPI, Spring Boot, Flask, Django, Pydantic \\
      \textbf{AI/ML Frameworks:} LangChain, LangGraph, Ollama, LangSmith, TensorFlow, Gemini CLI, Claude Code, n8n \\
      \textbf{Databases \& Storage:} MySQL, PostgreSQL, MongoDB, Redis, AWS S3 \\
      \textbf{DevOps \& Tools:} Git, Docker, GitHub Actions, AWS EC2, RabbitMQ
    }
  }
\end{itemize}

\end{document}
